### 2014-06-28 dicook/gender.Rmd
checking weights, in gender.Rmd

student2012.sub <- student2012[, c(1, 12, 501, 541, 546)]

@@

@@

                  mathgap=mean(PV1MATH[ST04Q01=="Male"], na.rm=T)-mean(PV1MATH[ST04Q01=="Female"], na.rm=T),

@@

>>>>

student2012.sub <- student2012[, c(1, 12, 501, 541, 546, 634)]

@@

student2012.sub$SENWGT_STU <- as.numeric(student2012.sub$SENWGT_STU)

@@

                  mathgap=mean(PV1MATH[ST04Q01=="Male"], na.rm=T)-
                          mean(PV1MATH[ST04Q01=="Female"], na.rm=T),
                  wmathgap=weighted.mean(PV1MATH[ST04Q01=="Male"], w=SENWGT_STU[ST04Q01=="Male"], na.rm=T)-
                          weighted.mean(PV1MATH[ST04Q01=="Female"], w=SENWGT_STU[ST04Q01=="Female"], na.rm=T),

@@

qplot(mathgap, wmathgap, data=student2012.sub.summary.gap, xlab="Mean", ylab="Weighted Mean",
      xlim=c(-30,30), ylim=c(-30,30)) + geom_abline(slope=1) + theme(aspect.ratio=1)

### 2014-06-28 dicook/school_matters.Rmd
checking weights, in gender.Rmd

df = scores_by_school %>% left_join(school2012.sub)
df$SC14Q02 <- factor(df$SC14Q02, labels=c(0,1,2,3))
df$SC14Q07 <- factor(df$SC14Q07, labels=c(0,1,2,3))
df$SC14Q10 <- factor(df$SC14Q10, labels=c(0,1,2,3))
df.mshort <- df[!is.na(df$SC14Q02),] %>% group_by(CNT, SC14Q02) %>% summarise(mmath2 = mean(mmath, na.rm=T))
qplot(SC14Q02, mmath2, data = df.mshort, facets = ~CNT, 
      xlab="Math teacher shortage (0=None, 1=Very little, 2=To some extent, 3=A lot)", 
      ylab="Math Score", geom=c("point","line"), group=CNT)
df.lshort <- df[!is.na(df$SC14Q10),] %>% group_by(CNT, SC14Q10) %>% summarise(mmath2 = mean(mmath, na.rm=T))
qplot(SC14Q10, mmath2, data = df.lshort, facets = ~CNT, 
      xlab="Library shortages (0=None, 1=Very little, 2=To some extent, 3=A lot)", 
      ylab="Math Score", geom=c("point","line"), group=CNT)
df2 <- summarise(group_by(df[!is.na(df$SC14Q02),], CNT, SC14Q02), teachers = mean(mmath, na.rm=T))
colnames(df2)[2] <- "levels"
df3 <- summarise(group_by(df[!is.na(df$SC14Q07),], CNT, SC14Q07), computers = mean(mmath, na.rm=T))
colnames(df3)[2] <- "levels"
df4 <- summarise(group_by(df[!is.na(df$SC14Q10),], CNT, SC14Q10), libmaterials = mean(mmath, na.rm=T))
colnames(df4)[2] <- "levels"
df.all <- merge(df2, df3)
df.all <- merge(df.all, df4)
df.m <- melt(df.all, id=c("CNT", "levels"))
colnames(df.m)[4] <- "math"
qplot(levels, math, data = df.m, facets = ~CNT, 
      xlab="Shortages (0=None, 1=Very little, 2=To some extent, 3=A lot)", 
      ylab="Math Score", geom=c("point","line"), group=variable, colour=variable) +
      scale_colour_manual("Type", values=c("teachers"="#1B9E77", "computers"="#D95F02", "libmaterials"="#7570B3")) +
      theme(legend.position="bottom") 
#ggsave("shortages.pdf", width=14, height=14)
qplot(SC14Q02, data=df, geom="histogram", xlab="Teacher shortage", colour=I("#1B9E77"))
#ggsave("teacher-shortages.pdf", width=5, height=5)
qplot(SC14Q07, data=df, geom="histogram", xlab="Computer shortage")
#ggsave("computer-shortages.pdf", width=5, height=5)
qplot(SC14Q10, data=df, geom="histogram", xlab="Library materials shortage")
#ggsave("library-shortages.pdf", width=5, height=5)
```

>>>>

df = scores_by_school %>% left_join(school2012.sub)
df$SC14Q02 <- factor(df$SC14Q02, labels=c(0,1,2,3))
df$SC14Q07 <- factor(df$SC14Q07, labels=c(0,1,2,3))
df$SC14Q10 <- factor(df$SC14Q10, labels=c(0,1,2,3))
df.mshort <- df[!is.na(df$SC14Q02),] %>% group_by(CNT, SC14Q02) %>% summarise(mmath2 = mean(mmath, na.rm=T))
qplot(SC14Q02, mmath2, data = df.mshort, facets = ~CNT, 
      xlab="Math teacher shortage (0=None, 1=Very little, 2=To some extent, 3=A lot)", 
      ylab="Math Score", geom=c("point","line"), group=CNT)
df.lshort <- df[!is.na(df$SC14Q10),] %>% group_by(CNT, SC14Q10) %>% summarise(mmath2 = mean(mmath, na.rm=T))
qplot(SC14Q10, mmath2, data = df.lshort, facets = ~CNT, 
      xlab="Library shortages (0=None, 1=Very little, 2=To some extent, 3=A lot)", 
      ylab="Math Score", geom=c("point","line"), group=CNT)
df2 <- summarise(group_by(df[!is.na(df$SC14Q02),], CNT, SC14Q02), teachers = mean(mmath, na.rm=T))
colnames(df2)[2] <- "levels"
df3 <- summarise(group_by(df[!is.na(df$SC14Q07),], CNT, SC14Q07), computers = mean(mmath, na.rm=T))
colnames(df3)[2] <- "levels"
df4 <- summarise(group_by(df[!is.na(df$SC14Q10),], CNT, SC14Q10), libmaterials = mean(mmath, na.rm=T))
colnames(df4)[2] <- "levels"
df.all <- merge(df2, df3)
df.all <- merge(df.all, df4)
df.m <- melt(df.all, id=c("CNT", "levels"))
colnames(df.m)[4] <- "math"
qplot(levels, math, data = df.m, facets = ~CNT, 
      xlab="Shortages (0=None, 1=Very little, 2=To some extent, 3=A lot)", 
      ylab="Math Score", geom=c("point","line"), group=variable, colour=variable) +
      scale_colour_manual("Type", values=c("teachers"="#1B9E77", "computers"="#D95F02", "libmaterials"="#7570B3")) +
      theme(legend.position="bottom") 
#ggsave("shortages.pdf", width=14, height=14)
qplot(SC14Q02, data=df, geom="histogram", xlab="Teacher shortage", fill=I("#1B9E77"))
#ggsave("teacher-shortages.pdf", width=5, height=5)
qplot(SC14Q07, data=df, geom="histogram", xlab="Computer shortage", fill=I("#D95F02"))
#ggsave("computer-shortages.pdf", width=5, height=5)
qplot(SC14Q10, data=df, geom="histogram", xlab="Library materials shortage", fill=I("#7570B3"))
#ggsave("library-shortages.pdf", width=5, height=5)
```
